\mytitle

### 2016-06-12 report/paper.tex
Work on the paper

\caption{Balls-and-Bins \autocite{bnb} \todo[inline] {FIX IMAGE}}

@@

\subsection{Ordering Component}
The Ordering component is responsible for ordering events before delivering them to the application.
To achieve this, the Ordering component has a \textit{received} hash table of (\textit{id}, \textit{event}) pairs containing all the events which are received by the peer, but not yet delivered to the application and a \textit{delivered} hash table containing all the events which were delivered.
\par
In brief, the Ordering component first increments the timestamp of all the events which have been received in previous rounds to indicate the start of a new round. Then, it processes new events in the received ball by discarding events that have been received already (delivered events or events with timestamp smaller than the last delivered event). This is done to prevent delivering duplicate events. The remaining events in the received ball will be added to the \textit{received} hash table, and wait to be delivered based on the Stability oracle.
\subsection{Stability Oracle}
The Stability oracle is the component that outputs timestamps. It will increment its local clock every round as well as synchronize itself using timestamps of newly received events, to make sure the local clock does not drift too much.
\par
This Stability oracle offers an API to the Ordering component letting it know when an event is mature enough to be delivered to the application.
\par
As this component is local and only corrects itself when we receive new events, it generates no network traffic. This means it does not impact the scalability of EpTO.
\section{Performance Comparisons}
In the following subsections, we will present the results obtained for the different tests ran and explain their meanings.
\subsection{Methodology}
\label{sub:metho}
Our tests are run on a cluster provided by the University of Neuchâtel. For setting up our testbed we use OpenNebula \autocite{opennebula} to manage our cluster of virtual machines. We make use of Docker \autocite{docker}, More specifically we use Docker-compose. Docker-compose is a tool to run multi-container applications, coupled to docker-swarm, which lets us make a pool of Docker hosts appear as a single Docker host.
\par
Each peer is hosted in a Docker container in order to be isolated from other peers. We want to test and compare JGroups and EpTO and find at which point JGroups breaks in terms of latency and throughput. At this point EpTO should still be working. Under this treshold, JGroups should be faster than EpTO but EpTO should still hold its own.
\par
To measure the throughput, we transmit a certain number of events by certain number of peers in a defined period of time, and then we measure number of packets transmitted over the network.
\par
To measure the latency of both protocols, we measure the average time difference between broadcasting an event by a peer, and delivering the same event by the same peers. In this way we can have an estimation of the approximate delay, and compare two protocols.
\subsection{Peer membership known}
\todo[inline]{We will present the results obtained and try to explain the results}

\section{Future Works}
Future works will include testing, EpTO while having unknown peer membership. To account for that, we will need to modify NeEM to support the use of a Peer Sampling Service. We plan on implementing the CYCLON Peer Sampling Service \autocite{Voulgaris2005}.

@@

% use section* for acknowledgement
\section*{Acknowledgment}
This research was under supervision and help of one of the creators of EpTO algorithm, Dr. Hugues Mercier. We 	thank Dr. Miguel Matos, another creator of EpTO and one the creators of NeEM library, who provided us insight and expertise that greatly assisted us during the research.
\par`
We also like to thank Valerio Schiavoni to provide us the access to the cluster of University of Neuchâtel.

>>>>

\caption{Balls-and-Bins \autocite{bnb}}

@@

\subsection{Ordering Component}
The Ordering component is responsible for ordering events before delivering them to the application.
To achieve this, the Ordering component has a \textit{received} hash table of (\textit{id}, \textit{event}) pairs containing all the events which are received by the peer, but not yet delivered to the application and a \textit{delivered} hash table containing all the events which were delivered.
\par
In brief, the Ordering component first increments the timestamp of all the events which have been received in previous rounds to indicate the start of a new round. Then, it processes new events in the received ball by discarding events that have been received already (delivered events or events with timestamp smaller than the last delivered event). This is done to prevent delivering duplicate events. The remaining events in the received ball will be added to the \textit{received} hash table, and wait to be delivered based on the Stability oracle.
\subsection{Stability Oracle}
The Stability oracle is the component that outputs timestamps. It will increment its local clock every round as well as synchronize itself using timestamps of newly received events, to make sure the local clock does not drift too much.
\par
This Stability oracle offers an API to the Ordering component letting it know when an event is mature enough to be delivered to the application.
\par
As this component is local and only corrects itself when we receive new events, it generates no network traffic. This means it does not impact the scalability of EpTO.
\section{Performance Comparisons}
In the following subsections, we will present the results obtained for the different tests ran and explain their meanings.
\subsection{Methodology}
\label{sub:metho}
Our tests are run on a cluster provided by the University of Neuchâtel. For setting up our testbed we use OpenNebula \autocite{opennebula} to manage our cluster of virtual machines. We make use of Docker \autocite{docker}, more specifically we use Docker-compose. Docker-compose is a tool to run multi-container applications, coupled to docker-swarm, which lets us make a pool of Docker hosts appear as a single Docker host.
\par
Each peer is hosted in a Docker container in order to be isolated from other peers. We want to test and compare JGroups and EpTO and find at which point JGroups breaks in terms of latency and throughput. At this point EpTO should still be working. Under this treshold, JGroups should be faster than EpTO but EpTO should still hold its own.
\par
To measure the throughput, we transmit a certain number of events by certain number of peers in a defined period of time, and then we measure number of packets transmitted over the network.
\par
To measure the latency of both protocols, we measure the average time difference between broadcasting an event by a peer, and delivering the same event by the same peers. In this way we can have an estimation of the approximate delay, and compare two protocols.
\subsection{Peer membership known}
\todo[inline]{We will present the results obtained and try to explain the results}

\section{Future Works}
One of the student working on this project will do his master thesis on this project.

Future works will include testing EpTO while having unknown peer membership. To account for that, we will need to modify NeEM to support the use of a Peer Sampling Service. We plan on implementing the CYCLON Peer Sampling Service \autocite{Voulgaris2005}. For now, we plan on using a tracker as in torrents to give each peer its initial view. This tracker is already implemented and works as a python web server that gets all alive peers and randomly select $K$ peers and sends this result to the EpTO peer.

@@

% use section* for acknowledgement
\section*{Acknowledgment}
This research was under supervision and help of one of the creators of EpTO algorithm, Dr. Hugues Mercier. We 	thank Dr. Miguel Matos, another creator of EpTO and one the creators of NeEM library, who provided us insight and expertise that greatly assisted us during the research.
\par`
We would also like to thank Valerio Schiavoni to provide us the access to the cluster of University of Neuchâtel as well as Sebastien Vaucher for the help with setting up Docker and Docker Swarm.
